\section{Background and requirements} % (fold)
\label{sec:background}

As already mentioned in the introduction, the project deals with the realisation of
a tool that simulates today's food delivery systems. The projet requires to have five main 
actors being the users: \Restaurant, \Customer, \Manager, \Courier~and the system: \Core.

A restaurant offers different \Meal~, being either a \HalfMeal~or a  
\FullMeal. A \FullMeal~ is made of a \Starter, a \MainDish~and a \Dessert. The \HalfMeal~ consists 
of a \MainDish~and either a \Starter~ or a \Dessert. Additionally each restaurant offers a \Menu~containing 
a list of \Starter~, \MainDish~ and \Dessert, so that a \Meal can be chosen à la carte. 

A \Customer can choose one of three different \emph{fidelity card plans} that allow him to some kind of reduction 
according to chosen \emph{fidelity card plan} \ref{sub:fidcardplan}.

All users contain basic attributes like a name, a surname, etc. and have distinctive functions that are described 
in detail below \ref{sub:users}.

Moreover, the system implements different \emph{target profit policies}, \emph{delivery policies}, \emph{shipped order policies}
also being described in detail below \ref{sub:policies}.

Let's take a more detailed look at the core, the different actors, the fidelity card plan and the supported policies.

\subsection{Core system} % (fold)
\label{sub:core_system}
The following paragraph contains concise description  
of the different requirements needed for the core.

\vspace{0.3\baselineskip}

\begin{itemize}
  \begin{minipage}{0.47\linewidth}
    \item setting of the service-fee, the markup percentage and the delivery cost
    \item allocating \Courier~depending on the shipped order policy \ref{sub:policies}
    \item notifying \Customer~if enabled by him
  \end{minipage}
  \begin{minipage}{0.53\linewidth}
   \item computing total income 
   \item choosing target profit policy \ref{sub:policies}
  \end{minipage}
\end{itemize}


\subsection{Users} % (fold)
\label{sub:users}
The following paragraphs contain concise descriptions
of the different most important requirements needed for every \User.


\paragraph{Manager}~\vspace{0.3\baselineskip}
\begin{itemize}
  \begin{minipage}{0.47\linewidth}
    \item add/remove \User
    \item activate/deactivate \User
    \item profit related attribute
    \item income over period
    \item income per \Customer
  \end{minipage}
  \begin{minipage}{0.53\linewidth}
    \item target profit policy
    \item most selling \Restaurant
    \item most active \Courier
    \item setting delivery policy
  \end{minipage}
\end{itemize}

\paragraph*{Restaurant}~\vspace{0.3\baselineskip}
\begin{itemize}
  \begin{minipage}{0.47\linewidth}
    \item add/remove \Dish
    \item add/remove \Meal
    \item add/remove \Meal~of the week
  \end{minipage}
  \begin{minipage}{0.53\linewidth}
    \item set \lstinline|discountFactors|
    \item sort of shipped orders following policy \ref{fid_card_plan}
  \end{minipage}
\end{itemize}

\paragraph*{Customers}~\vspace{0.3\baselineskip}
\begin{itemize}
  \begin{minipage}{0.47\linewidth}
    \item place \Order
    \item choose fidelity plan option \ref{fid_card_plan}
    \item get history of orders
  \end{minipage}
  \begin{minipage}{0.53\linewidth}
    \item get info about fidelity plan and points
    \item access and modify account info
    \item give/remove consensus for notification
  \end{minipage}
\end{itemize}

\paragraph*{Couriers}~\vspace{0.3\baselineskip}
\begin{itemize}
  \begin{minipage}{0.47\linewidth}
    \item register/unregister their account
    \item set their state
  \end{minipage}
  \begin{minipage}{0.53\linewidth}
    \item change their position
    \item accept/refuse to a delivery call
  \end{minipage}
\end{itemize}

\subsection{Policies} % (fold)
\label{sub:policies}
The following paragraph contains concise description  
of the different policies.

\paragraph{Target profit policies}~\vspace{0.3\baselineskip}
Two out of the three profit related quantities: \emph{service-fee, the markup percentage, the delivery cost}
are taken as given inputs depending on the chosen \emph{target policy} as well as an expected profit. The functions implemented
by each policy allow the \Manager to simulate the third profit related quantity that is not taken as an input and thus 
needed to achieve the profit. The profit is calculated as follows: 
\[ profit for one order = order price * markup percentage + service fee - delivery cost \] 

\begin{itemize}
    \item \emph{targetProfit DeliveryCost}: the delivery cost is simulated.
    \item \emph{targetProfit ServiceFee}: the service fee is simulated.
    \item \emph{targetProfit Markup}: the markup percentage is simulated.
\end{itemize}

\paragraph{Delivery policies}~\vspace{0.3\baselineskip}
The delivery policies define in which way the \Core choses the courier for a placed order.

\begin{itemize}
    \item \emph{fastest delivery}: The courier having the shortest distance to the selected restaurant is chosen.
    \item \emph{fair-occupation delivery}: The courier having executed the least amount of orders is chosen.
\end{itemize}

\paragraph{Shipped order sorting policies}~\vspace{0.3\baselineskip}
The \emph{shipped order sorting policies} allow restaurants and managers to sort the shipped orders according to different criterias.

\begin{itemize}
    \item \emph{most/least ordered Meal}: A ascending/descending list of all sold Meals
    \item \emph{most/least ordered dishes}: A ascending/descending list of all sold Dishes.
\end{itemize}

\subsection{Fidelity Card Plan} % (fold)
\label{sub:fid_card_plan}

Each customer can choose between three different fidelity card plans having each different bonuses.

\begin{itemize}
    \item \emph{Basic fidelity card}: The \Customer has access to a special offer provided by each restaurant.
    \item \emph{Point fidelity card}: The \Customer collects fidelity points and gets a certain reduction after 
	having reached a certain limit of points.
	\item \emph{Lottery fidelity card}: The \Customer takes part in a lottery and has the chance of getting his order for free.
\end{itemize}

\subsection{Summary}

In order to give a basic overview of the typical function, the ordering of a food item, we want to briefly summarize this process.
A \Client will place an \Order by choosing a one or more \Meal or one or more \Dish of a \Restaurant. The \Order containing all the 
necessary information is handed to the \Core. The \Core will treat the \Order by choosing a \Courier according to the \emph{Delivery policy}. 
The \Courier can either accept or decline the \Order. If any \Courier accepts the \Order, it is executed and saved in the \Core.

% subsection users (end)

% section background (end)
