\section{Implementation} % (fold)
\label{sec:implementation}

In order to effectively give an overview of the code implementation
and to describe the key points, we will take the following approach: 

\begin{enumerate}
	\item First, we will describe the general structure of the
  main \emph{packages} (see~\ref{sub:structure_of_the_main_packages}).
	\item Second, we will pick out \emph{key methods} of the packages
  and explain them in detail (see~\ref{sub:key_methods}). 
	\item Third, we will describe the most important functionality of the system :
  \emph{placing an order} and treating it afterwards (see~\ref{ssub:process_of_giving_up_an_order}).
\end{enumerate}

\subsection{Structure of the main packages} % (fold)
\label{sub:structure_of_the_main_packages}
Our java project contains in total nine packages.
The \exceptions~package will not be further explained as it is not too important.
The \parsers~and \txtF~ ones are there to create objects for the testing
and also need no further explanation.
The \userI~package is not relevant for the first part of the project
and will be described in the second part.
Lastly, the \tests~package will be explained in detail in the next section.
We will thus describe the \policies, \restaurantSetup, \policies, \tests~and
\users~packages. 

\subsubsection{Package core} % (fold)
\label{ssub:core}
The package \core~contains the classes \Core~and \Order~as can be seen in
the UML diagram in figure~\ref{fig:core_order_uml}. 

The core is the center of the application that \emph{connects all the users}.
To better understand the structure, please take a quick look at the UML diagram
in figure~\ref{fig:core_users_uml}. 
All classes that we made are there to give a certain functionality to a \User.
Since the \Core~contains a list of all \User, it is able to access all classes
and thus all the information that is saved in the system.
This characteristic is probably the most important one of our application since it allows us to

\begin{enumerate}
	\item handle all relevant functionalites over the \Core,
	\item ensure the open-close principle because we can easily decide
  which \User~has access to which functionality,
	\item and finally to take care that the structure is clear and well-organized.
\end{enumerate}

The \Order~class is there to present an actual made order.
An order is in some sense the way the different users ``communicate'' with restaurants.
Its most important functionalities will also be discussed throughoutly 
furter below (see~\ref{ssub:process_of_giving_up_an_order}).
It is important to understand the different price attributes that are in 
the state of \Order as can be seen in listing~\ref{lst:prices_order}.

\begin{enumerate}
	\item \lstinline|priceInter| is the part of the order price the restaurant will receive.
	\item \lstinline|priceFinal| is the actual price the customer pays \MyFoodora.
	\item \lstinline|profitFinal| is the profit \MyFoodora~makes with the order. 
\end{enumerate}

% subsubsection core (end)

\subsubsection{Package policies} % (fold)
\label{ssub:policies}

The package \policies~contains all the necessary policies that are needed
and whose designs were explained in the previous section.

Most of the policies follow the typical \emph{strategy pattern},
where an interface with the name of the actual policy is implemented by the corresponding
behaviours classes, as shown in the UML diagram in figure~\ref{fig:delivery_uml}.
The core then has an attribute where its declaration is the class name
and which then is a reference to one of the actual policies (see 
figure~\ref{fig:core_policies_uml}). 
Only the \lstinline|SortPolicy|~is not realised according to
the typical \emph{strategy pattern}
and uses an \emph{abstract class} instead of an interface.
The following paragraph explains why we choose to do it this way
and what advantages it brings to the solution.

\textit{At this point it has to be mentioned that we well understood the assignement
to only display \HalfMeal, but we are convinced that is more logical
and user friendly to present all \Meal~instead of only halfmeals.}

We thought about using the \lstinline|ArrayList<savedOrders>|
of the core that saves all orders ever having been executed 
to present how often a \Meal~or \Dish~was sold, but we decided against it since
\begin{enumerate}
	\item First, it is not easy to extract the needed information
  from \lstinline|savedOrders|~because it contains objects of type \Order.
	\item Second, a new \lstinline|List|~would have to be created
  that has to sort all the needed information.
\end{enumerate}
Therefore, we implemented two sorted \lstinline|TreeSet|, 
ie. a list that is \emph{always sorted} because it puts the added 
element directly at the right spot. 
The advantages are
\begin{enumerate}
	\item Each time the function is called there is no sorting needed in advance.
	\item A lot of coding was avoided and \emph{transparency} is improved.
\end{enumerate}

% subsubsection policies (end)

\subsubsection{Package restaurantSetUp} % (fold)
\label{ssub:restaurantsetup}

The package \restaurantSetup~contains all the classes that are needed
for a restaurant to function properly.
Its corresponding UML diagram can be seen in figure~\ref{fig:dish_meal_uml}.
In order to add dishes or meals, we used the already explained \emph{abstract
factory pattern}. The two other important structures of 
\restaurantSetup~are the class structures of \Meal~and \Dish. 

\Meal~is inheritated by \HalfMeal~and \FullMeal. 
It is important to know that even if the class \Meal~does not have to be abstract,
we declared it as an abstract class either way. 
The reason is that, we want to prevent other classes being able to 
create an instance of this type, as this have no meaning for the solution.
We make sure that a \FullMeal~is composed of exactly one \Starter,
one \MainDish~and one \Dessert~by declaring the parameters of the method
\lstinline|setFullMeal| respectively.
The same holds true for \HalfMeal~taking the respective requirements into account.

On the other side, \Dish~is inheritated by \Starter, \MainDish~and \Dessert.
All functionalities for the concrete dishes are the same so the same 
reasoning as explained for meals holds true. 

Lastly, it is to be noticed that a \Restaurant~offers either a \Meal~or
a self composed meal composed of different dishes of the menu.
That is why we used \emph{composition} by giving each \Restaurant~exactly
one \Menu~that contains all the single dishes being offered.
An object of type \Menu~contains therefore a list of starters, maindishes and desserts.
Additionally, is a list of all the provided meals included in each \Restaurant.

% subsubsection restaurantsetup (end)

\subsubsection{Package users} % (fold)
\label{ssub:users}

The package \users~contains all classes related to users of the system,
being ``\textit{the courier, the customer, the restaurant and the manager}''.
Each of them is inherited by \User~and therefore takes over certain 
necessary attributes like \lstinline|name| and \lstinline|messageBox|
which is a \lstinline|Stack| that contains all the messages intented for this \User.
Note that (as for the \Dish~and \Meal~classes), the \User~class is declared \emph{abstract},
preventing ``unintented users'' instanciation.
Additionally it is important that every \User~has the function \lstinline|update()|
that adds a message to its \lstinline|messageBox|, which is the reason 
why this method is also in the class \User.
Each \User~adds specific functions for its needed functionality.
We want to mention two important implementations
\begin{enumerate}
	\item \Courier~has a \lstinline|LinkedList| of received orders,
  where an \Order~is placed every time he has to deliver it.
	\item \Customer~implements the interface \lstinline|Observer|,
  as shown in figure~\ref{fig:users_uml}.
\end{enumerate}

\Manager~neither has many attributes, nor does it has many methods 
since all the functions used by \Manager~are in the \Core.

% subsubsection users (end)

% subsection structure_of_the_main_packages (end)
\subsection{Key methods} % (fold)
\label{sub:key_methods}


\subsubsection{Log-in functionality of the core} % (fold)
\label{ssub:log_in_functionality_of_the_core}

The \emph{log-in/log-out functionality} of the core is very important because it ensures 
that certain functions can only be accessed by certain users.
Let's take a closer look at the method \lstinline|logIn()| (see listing~\ref{lst:login}).
First the function checks whether the \lstinline|username|~is
registered and only if this holds true the \User~having this \lstinline|username| can log in.
Then the \lstinline|current_user| being an attribute of \Core~and
of type \User~is given the \User~that is associated to the \lstinline|username|
via the \lstinline|users HashMap|.
Now, the function checks which type of \User~has just logged in sets 
the respective ``current" attribute to the \User~being now logged in.

If for exemple a \Manager~logs in the attribute \lstinline|current_manager| will
be set to the \User, whereas the other ``current" attributes (respectively
\lstinline|current_customer|, \lstinline|current_restaurant|
and \lstinline|current_courrier|) stay equal to \lstinline|null|.
Finally the left messages for the logged-in \User~are displayed
via calling the method \lstinline|checkMessages|.

This system allows us to design pretty much every method in the core in a defensive way 
by containing a ``checker'' verifying who is actually logged-in, e.g.
\begin{center}
  \lstinline|if(current_customer != null){ doAction(); }|
\end{center}
Herewith, we can ensure that certain functions can only be used 
by certain \User~and that a log-in had to be performed before a \User~can use a method.

A point has to be made on the \emph{efficiency} of the login function, which
is somewhat important in such systems where the users don't want to wait
while logging in.
Indeed, the use of an \lstinline|HashMap| allows to check if username exists
in $\mathcal{O}(1)$ time on average and in $\mathcal{O}(\log{n})$ on worst case
(this happens when collisions happen, ie. the \lstinline|HashMap|
entries container is not big enough)\cite{hashMap}.

% subsubsection log_in_functionality_of_the_core (end)

\subsubsection{Fastest Delivery method of Delivery Policy} % (fold)
\label{ssub:fastest_delivery_method_of_delivery_policy}

The \emph{Fastest Delivery method} is presented at this point because it gives a good exemple of how the implementation of the \emph{Strategy pattern} actual works and also shows how this project allowed us to gain new skills in \lstinline|Java|. Please take a look at the following pseudo code in order to better understand the method that is talked about: 
\ref{lst:fast_deliv_meth}. 

To begin with, it can easily seen that the method is the method that has to be overridden due to the implementation of the interface \lstinline|DeliveryPolicy|. Every object that is declared as an \lstinline|DeliveryPolicy|~object thus has to have a function called \lstinline|howToDeliver|. So what does this function do? In short, this method takes a list of all couriers and an address (of a \Restaurant) as entries and returns a list of the same couriers sorted in ascending order according to the distance between the couriers address and the inserted restaurant's address. Let's dive into the code.

First the method calls another method called \lstinline|getDistance|~that takes the same entries as the \lstinline|howToDeliver|~method and gives back an \lstinline|ArrayList|~of type \lstinline|double|~containing the distances between each courier and the restaurant's address. The list is unsorted and looks for exemple as follows: \lstinline|{4.22, 8.9, 9.34, 8.3, ...}|. This method performs a simple calculation and will not be explained it detail.

Second comes the actual sorting part of the function. In the beginning, we did not find an efficient way to sort the couriers of list by a value that is not even an attribute of the object \Courier. After searching the internet, we discovered the \lstinline|Stream|~functionality of \lstinline|Java|~and after learning the basics of this Java8 extension saw in it a good solution to our problem. So, we initialise a \lstinline|Stream|~having the amount of members as there are couriers in the list and map each of those members to a new Object, called 
\lstinline|CourierDistance| that contains a \Courier~as well as a distance. We created this class to actually sort the \Courier~by their respective distance, being an external value that changes depending on the restaurants \lstinline|Address|. Now our stream is basically an unsorted list of objects of type \lstinline|CourierDistance|. The next step is to sort the list members according to their distances. Finally, the objects \lstinline|CourierDistance|~are mapped to the type \Courier~ and the \lstinline|Stream|~is transformed into an \lstinline|ArrayList|~that will be returned and used to chose the best fit courier for a specific order. 

The background of this method will be clearer after having read the third part of this section \ref{ssub:process_of_giving_up_an_order}. This code excerpt should have shown:

\begin{enumerate}
	\item how the \emph{Strategy pattern} works in practise and
	\item how we always looked for efficient code designing.
\end{enumerate}

% subsubsection fastest_delivery_method_of_delivery_policy (end)

\subsubsection{Add \FullMeal~method} % (fold)
\label{ssub:add_full_meal_method}

This section explaines how a restaurant will actually add a \FullMeal. In order to
create a \FullMeal, one creates a new \lstinline|MealFactory| as can been seen in
listing \ref{lst:createFactory}. Calling the \lstinline|static|
\lstinline|getFactory()| method with the parameter ``MEAL" returns a
\lstinline|MealFactory|. Having created the factory, the next step is to create 
the actual \FullMeal. The just created \lstinline|MealFactory| now enables one to
create an actual \Meal~as can be seen in listing \ref{lst:mealCreator}. Calling the
method \lstinline|getMeal()| with the name of the \Meal~and the parameter ``FULLMEAL"
returns finally a \FullMeal~that does not yet include the actual dishes belonging to
the meal. 

To complete the \FullMeal~the method \lstinline|setFullMeal()| with the three
parameters of type \Dish~ being notably \Starter, \MainDish and \Dessert~is called,
which can be seen in listing \ref{lst:SetFullMeal}. First, the three \Dish~are added to
the \FullMeal. Second, the method automatically recognizes whether all added dishes are
of the same type by a simple \lstinline|==| comparision and names the type of the
\Meal~accordingly. The \FullMeal~is finally completed and can be added to \Restaurant. 
The self-explanatory method of the class \Restaurant~can be seen in listing \ref{lst:addMeal}.

The question arises, whether it is really necessary to call that many methods only to 
have added a \FullMeal~to \Restaurant. This brings us to the disadvantage of
implementing the \emph{abstract factory pattern}. Having assessed the different
designing possibilities, we considered the easy-to-extend design of the 
\emph{abstract factory pattern} to be the best fit since a likely extension of the restaurant's offer (e.g. drinks) can very easily implemented. The slightly more complex process of creating a \FullMeal~is will stay unnoticed to the actual user because he will be guided by the system while inserting the needed information for a \FullMeal.

% subsubsection add_full_meal_method (end)

% subsection key_methods (end)

\subsection{Process of giving up an order} % (fold)
\label{ssub:process_of_giving_up_an_order}

In the last part of the implementation section, we quickly want to go through the most
important functions being placing an order and then treating it. 
So, making the hypothesis that a customer created an \Order~by having chosen a
\Restaurant~and having added all the necessary \Meal~or \Dish,
we start with the code \lstinline|placeOrder()| with the parameter \Order~ that can be
seen in listing \ref{lst:placeOrder}. 
The first lines of the code ensure as we explained earlier that a \Customer~is
actually logged in to give up an \Order~. The created order will be saved in the
\lstinline|LinkedList| \lstinline|receivedOrders| of the \Core. The Use of a
\lstinline|LinkedList| realises the so-called ``First-in-First-out", which is reasonable considering the fact that the oldest \Order~should be treated first.
Next, the \Customer~will be notified and the order can be treated.

Now, we arrive at the main method of the system the \lstinline|treatOrder()| method of
the \Core. Please take a look at both the simplified pseudo code that will be
clarified in the following - listing \ref{lst:treatOrder} - as well as the actual code
in the class \Core.

The function is declared \lstinline|private| so that the function can only be
called in the core and this is done solely by the function \lstinline|placeOrder()|.
This means that as soon as a logged-in \Customer~places an \Order~it will be taken
care of instantely, so that in the current version of our system each \Order~that is
placed in the list of \lstinline|receivedOrders| is removed and treaten on the spot.
A system extended to a multi-threaded one takes advantage of the implementation of
a list of \lstinline|receivedOrders|, whereas it is useless for the system as it is now. 

\begin{itemize}
	\item First, the oldest order is taken and will be treated. 
	\item Second, a list of couriers is generated according to the current
		\lstinline|DeliveryPolicy| whose exact functioning is explained in the
		subsubsection \ref{ssub:fastest_delivery_method_of_delivery_policy}.
	\item Third, now that we have a list of courier we will contact them one by one
		according to the order of the courier list until either a \Courier~accepted
		the \Order~or there are currently no \Courier~available. This means a
		\Courier~is set to the current courier. Then this \Courier~can either accept
		or decline the \Order. Since the system is a single-threaded system, we use a
		function that randomely makes the courier accept/decline the \Order. Finally,
		the \Courier~is removed from the list.
	\item Forth, if all \Courier~delined, the system will notify the \Customer,the
		\Order~will be deleted and the method finishes.
	\item Fifth, if a \Courier~was found, the final price of the order will be saved
		as an attribute of the \Order. Lastely the \Order~is saved and all related
		users will be notified.	
\end{itemize}

This pseudo code is a quite simplified version of the real code, but explains well the
most important functioning.

% subsection place_and_treat_order (end)


% section implementation (end)