\section{Conclusion and further work} % (fold)
\label{sec:conclusion}
We have now defined the necessary \emph{background} to understand
what the \emph{requierements} were about and explained how we \emph{designed} 
our solution to meet them. We also described how this 
\emph{implementation} was conducted effectively throughout the code
and what \emph{testing} methods have been used to ensure stability
and correctness.
How the two user interfaces have been built has then been described
as well as the results brought by combining those to the core system.

As we are writting those last lines of the project, we wonder what
could be done as further work.
Considering that we implemented \emph{serialization} of the core
in both interfaces in order to efficiently remember the state
of all users, orders and any other thing related to the core,
we might consider some security related problems that might
appear when extending the solution to be multi-user.
In this case, it will indeed be necessary to consider a safer
way to serialize the data so that nothing can be lost even
if bad handling or system crashes happens.

Speaking of multi-user system, this is also something our system
might need to include.
This will need multithreading programming and thus reorganise
the classes to allow multiple users to be logged in at the same
time, all of this considering that information has to be
confidential and securely stored. 

Finally, we can consider extensions of the functions of the system itself
such as being able to serve drinks or adding a payement system.
As we designed our solution following well known design patterns,
those extensions will appear to be relatively easy to implement.
Crawling through the web, we realised that those patterns were something
important in the software engineering world and we are glad this
project has let us the chance to understand it practically.

% section conclusion (end)